### 2022-01-09 README.Rmd
update README
- Only 4 columns in head(dataset)

head(dataset[, 1:5], n = 5) # Print the first 5 rows and columns
```

For more information about the dataset, you can consult the package documentation.

>>>>

head(dataset[, 1:4], n = 5) # Print the first 5 rows of the first 4 columns
```

For more information about the dataset, you can consult the package [documentation](https://nim-ach.github.io/ASQ3/reference/dataset.html).
